Topological Sigma Models for Generalized Para-Complex Geometry

### 2020-01-31 newdraft.tex
changes in section 2 and 3
mainly added para-complexified versions of things, went through around 1/2 of sec. 3

\subsubsection{Para-Complexified Version}
In order to make the analogy between complex and para-complex geometry more explicit, one can \textit{paracomplexify} all objects by tensoring with the algebra $\mathbf{C}$ of \textbf{para-complex numbers}, which are given by ordered pairs $(x,y)\in \mathbb{R}\otimes (1,k)$ generated by $1$ and the symbol $k$, satisfying $k^2=1$ and called the para-complex unit. The elements $(x,y)\in \mathbf{C}$ can be therefore written as
\begin{align*}
\mathbf{C} \ni z=(x,y)=x+k\cdot y.
\end{align*}
On $\mathbf{C}$, we define the following familiar operations:\begin{align}
\begin{aligned}
&\bullet\quad \text{Para-complex conjugation: }x+\kk y\mapsto \overline{x+\kk y}=x-\kk y\\
&\bullet\quad \text{Real part: } x+\kk y \mapsto \text{Re}(x+\kk y)=x\\
&\bullet\quad \text{Imaginary part: } x+\kk y \mapsto \text{Im}(x+\kk y)=y.
\end{aligned}
\end{align}

@@

\newcommand{\Cp}{{\mathbf{C}}}
The isomorphism of para-complex vector spaces \eqref{para-complexification} induces an isomorphism between $\Lambda^{(p,q)}(T^*\PS)$ and $\Lambda^{p,q}(T^*\PS^\mathbf{C})$ as well as between the sections $\Omega^{(p,q)}$ and $\Omega_\Cp^{p,q}$, where the bigrading of the real bundle is with respect to the $\pm 1$ eigenvalues of $K$, while the bigrading of the para-complexified bundle is with respect to the $\pm k$ eigenvalues of $K$. Explicitly, we have
\begin{align}\label{isom_bigradings1}
\phi:\ (\ap,\tl{\ap})\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}\longmapsto \frac{1+k}{2}\ap + \frac{1-k}{2}\tl{\ap}\ \in\ \Omega_\Cp^{p,q}
\end{align}
with the inverse
\begin{align}\label{isom_bigradings2}
\phi^{-1}:\ \bm{\ap}\ \in\ \Omega_\Cp^{p,q}\longmapsto (\text{Re}(\bm{\alpha})+\text{Im}(\bm{\ap}),\text{Re}(\bm{\alpha})-\text{Im}(\bm{\ap}))\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}.
\end{align}
The point we would like to emphasize here is that to one para-complex differential form of degree $p,q$ corresponds a {\it pair} of real forms in degrees $(p,q)$ and $(q,p)$. In particular, a para-complex form in degree $k,0$ corresponds to a pair of forms in degrees $(k,0)$ and $(0,k)$, i.e. a two $k$-forms on the two canonical para-complex foliations. Consequently, recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can easily deduce that the corresponding {\bf para-complexified Dolbeault complex} is given by
\begin{align}
\left( \Omega^{0,\bullet}_\Cp,\bar{\p}^\Cp\right),
\end{align}
In particular, the condition of holomorphicity in the para-complex coordinates $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ and $\bar{z}^i$ is equivalent to a local independence of the coordinates $\bar{z}^i$ and is therefore entirely analogous to complex geometry.
%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}

@@

\subsubsection{Lie algebroids of a para-complex manifold}\label{lie_algds_paracpx}
Here we briefly discuss what Lie algebroids the para-complex structure on a manifold $\PS$ gives rise to.
%First, we recall that a Lie algebroid over $\PS$ is the triple $(E,a,\brac_E)$, where $E\rightarrow \PS$ is a vector bundle, $a: E\rightarrow T\PS$ is a bundle map and $\brac$ is a bracket operation on the sheaf of sections of $E$. The three satisfy the following:
%\begin{enumerate}
%\item $a([e_1,e_2]_E)=[a(e_1),a(e_2)]$, $\brac$ being the Lie bracket on $T\PS$,
%\item $[e_1,fe_2]_E=f[e_1,e_2]_E+a(e_1)[f]e_2$.
%\end{enumerate}

@@

If we now consider the para-complexified tangent bundle $T\PS_\Cc$, we get a para-complex Lie algebroid, which can be understood as certain sense as a {\it sum} of the two above Lie algebroids:
\begin{Ex}[Para-holomorphic tangent bundle]\label{ex:para-hol-tangent}
The $+k$-eigenbundle $T^{1,0}\subset T\PS_\Cc$ is a para-complex Lie algebroid with the bracket given by the extension of the usual Lie bracket to $T\PS_\Cc$ and restricted to $T^{1,0}$ and the anchor is again the inclusion $\imath:\  T^{1,0}\hookrightarrow T\PS_\Cc$. We can identify $T\PS_\Cc=T\oplus k T$, so that a section $X\in \XX_\Cc(\PS)$ is written as $X=U+kV=(U,V)$ for $U,V \in \XX(\PS)$ real vector fields and the Lie algebroid bracket is then given in terms of the usual Lie bracket of real vector fields as
\begin{align*}
[(U,V),(U',V')]=([U,U']+[V,V'],[U,V']+[V,U']).
\end{align*}
The Chevalley-Eilenberg complex is the para-complexified Dolbeault complex \eqref{para-dolbeault}.

There is an analogous map to \eqref{isom_bigradings2} for vector fields (which we also denote $\phi^{-1}$) mapping $X \in \XX^{1,0}_\Cc(\PS)$ to a pair of vector fields
\begin{align*}
X=(U,V) \overset{\phi^{-1}}{\mapsto} (U+V,U-V) \in \XX^{(1,0)}(\PS)\otimes \XX^{(0,1)}(\PS),
\end{align*}
realizing the $\mathbb{R}$-linear isomorphism between $T^{1,0}$ and $T\PS=L\oplus \Lt$. This map can be used to map the para-complex Lie algebroid $T^{1,0}$ with a pair of real Lie algebroids. It is a simple exercise to check that $\phi^{-1}$ in fact maps to the pair of real Lie algebroids described in Example \ref{ex:real-lie-algds-on-paracpx}, so that the following diagram commutes
\begin{equation*}
\begin{tikzcd}
T^{1,0} \arrow[hookrightarrow]{d}{\imath}\arrow{r}{\phi^{-1}} & L\oplus \Lt\arrow[hookrightarrow]{d}{\imath_L\oplus\imath_\Lt}\\
TP_\Cc \arrow{r}{(\text{Re},\text{Im})} & T\oplus T
\end{tikzcd}\ .
\end{equation*}
Note, however, that $L\otimes \Lt=T$ here is not a Lie algebroid (and in particular is not the tangent Lie algebroid) because the direct sum of anchors $\imath_L\oplus \imath_\Lt$ maps into $T\oplus T$ as opposed to $T$.

Consequently, the Chevalley-Eilenberg complex then also splits and can be understood as a direct sum of the two complexes corresponding to $L$ and $\Lt$, as denoted in \eqref{para-dolbeault}.
\end{Ex}

@@

\begin{Ex}[The trivial structure and its deformations]\label{ex:GpC_trivial}
Any manifold supports the following GpC structure
\begin{align*}
\KK_0=
\begin{pmatrix}
\id & 0 \\
0 & -\id
\end{pmatrix},
\end{align*}
that has eigenbundles $T$ and $T^*$ and is always integrable. The following two GpC structures can be seen as deformations of $\KK_0$ by either a two-form $b$ or a bi-vector $\beta$:
\begin{align*}
\KK_b=
\begin{pmatrix}
\id & 0 \\
2b & -\id
\end{pmatrix},\quad
\KK_\beta=
\begin{pmatrix}
\id & 2\beta \\
0 & -\id
\end{pmatrix}.
\end{align*} 
$\KK_b$ is integrable iff $\rd b =-H$, and its eigenbundles are $L_{b} = \text{graph}(b)=\{X+b(X)\mid X \in \XX\}$ and $\widetilde{L}_b =T^*$. Similarly, $\KK_\beta$ is integrable iff $\beta$ is a Poisson structure, (see \cite[Lemma~2.13]{Hu:2019zro}) and its eigenbundles are $L_\beta =T$ and $\widetilde{L}_\beta =\text{graph}(-\beta)=\{\ap-\beta(\ap)\}\mid \ap \in \Omega\}$.
The Lie algebroid $\Tilde{L}_{\beta}$ is equivalent to the Lie algebroid with underlying bundle $T^*$ and anchor given by the Poisson bivector $\beta : T^* \to T$. 
\end{Ex}

\begin{Ex}[Para-complex structures]\label{eg: pc}
An almost para-complex structure $K\in \Endo(T)$, defines the diagonal generalized almost para-complex structure:
\begin{align*}
\KK_K=
\begin{pmatrix}
K & 0 \\
0 & -K^*
\end{pmatrix}.
\end{align*}
The integrability of $\KK_K$ is equivalent to Frobenius integrability of $K$ , i.e. vanishing of the Nijenhuis tensor of $K$.
Thus a para-complex structure defines a generalized para-complex structure of the above form. 
The corresponding Dirac structures are given by the $+1$ eigenbundle $L_K =T^{(1,0)}\oplus T^{*(0,1)}$ and $-1$ eigenbundle $\widetilde{L}_K =T^{(0,1)}\oplus T^{*(1,0)}$, where the bigrading is with respect to $K$.
%
%The structure $\KK_P$ can be generalized to the following
%\begin{align*}
%\KK=
%\begin{pmatrix}
%P & \Pi \\
%\Omega & -P^*
%\end{pmatrix},
%\end{align*}
%where we can read off from the constraints in \eqref{eq:GpC_generalform} that $P^2=\id$ implies that $\Pi\Omega=0$ and both $\Pi$ and $\Omega$ have to be of type $(2,0)+(0,2)$ with respect to the grading given by $P$.
\end{Ex}

\begin{Ex}[Symplectic structures]\label{ex:GpC_sympl}
A pre-symplectic form $\omega$ defines the anti-diagonal almost generalized para-complex structure
\begin{align*}
\KK_\omega=
\begin{pmatrix}
0 & \omega^{-1} \\
\omega & 0
\end{pmatrix}.
\end{align*}
The integrability of $\KK_\omega$ is equivalent to $\rd\omega=0$.
Thus, if $\omega$ is symplectic then $\KK_\omega$ is a generalized para-complex structure.
The $\pm 1$ eigenbundles are given by $\text{graph}(\pm\omega)=\{X\pm\omega(X)\mid X\in \XX\}$.
\end{Ex}

\paragraph{Comparision with generalized complex structures}
Example \ref{ex:GpC_sympl} shows that a symplectic manifold $(M,\omega)$ is a GpC manifold and it is well-known \cite{Gualtieri:2003dx} that $(M,\omega)$ is also generalized complex (GC). However, while almost GC structures exist only on almost complex manifolds \cite{Gualtieri:2003dx}, Example \ref{ex:GpC_trivial} demonstrates that GpC structures exist on any Poisson manifold and in particular on any smooth manifold (with trivial Poisson structure). Another feature of GpC geometry that is not present in GC geometry is that the GpC structures can be half-integrable (similarly to ordinary para-complex structures): see the cases of $\KK_b$ and $\KK_\beta$ from Example \ref{ex:GpC_trivial} which are always at least half integrable and are fully integrable iff $b$ is closed and $\beta$ is Poisson, respectively. On the other hand, $\KK_\omega$ in Example \ref{ex:GpC_sympl} can only be half-integrable when the $H$-flux is non-zero.

@@

@@

In this section we will see how to associate a class of $2D$ topological field theories to generalized para-complex structures.
The construction closely follows the relationship between ordinary (non-para) generalized complex structures \cite{Gualtieri:2003dx} and $2D$ topological field theories developed in \cite{Cattaneo:2009zx, Pestun:2006rj}.
For another class of $2D$ boundary theories to the $3D$ Courant algebroid $\sigma$-model see \cite{SeveraTduality}. \btd{Please add any more references you think fit.}

For us, the prescription of defining the $2D$ topological theory associated to a generalized para-complex structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
More generally, this $3D$ theory can be defined for any Courant algebroid on $M$ \cite{Roytenberg:2002nu}, but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
The key to our construction is to realize the data of a generalized para-complex structure in terms of its eigenbundles, which are Dirac structures in the real Courant algebroid $\TT$.
More precisely, we obtain a pair of Dirac structures $L, \Tilde{L}$ corresponding to the $\pm$ eigenbundles of the generalized para-complex structure.

@@

By similar reasoning, one can obtain a single $2D$ TFT from the data of a generalized para-complex structure. 
One considers the para-complexification $(\TT) \otimes_{\RR} \Cc$ of the standard Courant algebroid. 
The real Dirac structures $L, \Tilde{L}$ combine to give a para-complex Dirac structure $L \oplus \Tilde{L}$. 
In turn, we obtain a single $2D$ TFT defined over the para-complex numbers.

@@

From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
We recall the construction of the $3D$ topological field theory from the data of a Courant algebroid. 
For other references, see \cite{Roytenberg:2002nu, Cattaneo:2009zx}.

@@

We begin by setting up our model for the theory of derived manifolds. 
For us, this is a well-behaved class of $NQ$ manifolds which are appropriate for setting up quantization of $\sigma$-models, see for instance \cite{CostelloSUSY}. 
A dg manifold is a pair $\cN = (N, \sA^*_\cN)$ where $N$ is a smooth manifold, called the body, and $\sA^*_\cN$ a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_N$.
Here, $\d_\cN$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
\begin{itemize}
\item[(1)] $\sA_\cN$ is concentrated in finitely many degrees;
\item[(2)] For each $k$, $\sA^k_\cN$ is a locally free sheaf of $C^\infty_N$-modules of finite rank;
\item[(3)] The differential $\d_N : \sA_\cN^* \to \sA_\cN^{*+1}$ is square zero differential operator making $(\sA_\cN , \d_\cN)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_N$.
\end{itemize}

In particular, as a graded algebra $\sA^*_\cN$ is given by functions on the total space of some graded vector bundle $A_\cN$ on $N$ (which is of finite rank and concentrated in finitely many degrees). 
In the language of $NQ$ manifolds, the homological vector field defining the $Q$-structure is $\d_\cN$.

@@

\begin{remark}
In \cite{PymSafronov} it was shown that a more general class of $2$-shifted symplectic derived spaces, called $L_\infty$ algebroids, are equivalent to {\em twisted} Courant algebroids. 
This is similar to a Courant algebroid, where the Jacobi identity only holds up to homotopy given by some closed $4$-form. 
\end{remark}

@@

From here on, to any Courant algebroid $E$ on a manifold $M$ we associate the dg manifold $X_E$ which carries a $2$-shifted symplectic structure. 
In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.

We first review some basic examples of AKSZ theories associated to Courant algebroids. 
The simplest type of Courant algebroid is one over a point, see Example \ref{Ex: point}. 
The resulting AKSZ theory is a familiar one.

>>>>

\subsubsection{Para-complexified picture}
In order to make the analogy between complex and para-complex geometry more explicit, one can \textit{paracomplexify} all objects by tensoring with the algebra $\mathbf{C}$ of \textbf{para-complex numbers}, which are given by ordered pairs $(x,y)\in \mathbb{R}\otimes (1,k)$ generated by $1$ and the symbol $k$, satisfying $k^2=1$ and called the para-complex unit. The elements $(x,y)\in \mathbf{C}$ can be therefore written as
\begin{align*}
\mathbf{C} \ni z=(x,y)=x+k\cdot y.
\end{align*}
On $\mathbf{C}$, we define the following familiar operations:\begin{align}
\begin{aligned}
&\bullet\quad \text{Para-complex conjugation: }x+\kk y\mapsto \overline{x+\kk y}=x-\kk y\\
&\bullet\quad \text{Real part: } x+\kk y \mapsto \text{Re}(x+\kk y)=x\\
&\bullet\quad \text{Imaginary part: } x+\kk y \mapsto \text{Im}(x+\kk y)=y.
\end{aligned}
\end{align}

@@

\newcommand{\Cp}{{\mathbf{C}}}
\subsubsection{Isomorphism between the real and para-complexified pictures}
The isomorphism of para-complex vector spaces \eqref{para-complexification} induces an isomorphism between $\Lambda^{(p,q)}(T^*\PS)$ and $\Lambda^{p,q}(T^*\PS^\mathbf{C})$ as well as between the sections $\Omega^{(p,q)}$ and $\Omega_\Cp^{p,q}$, where the bigrading of the real bundle is with respect to the $\pm 1$ eigenvalues of $K$, while the bigrading of the para-complexified bundle is with respect to the $\pm k$ eigenvalues of $K$. Explicitly, we have
\begin{align}\label{isom_bigradings1}
\phi:\ (\ap,\tl{\ap})\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}\longmapsto \frac{1+k}{2}\ap + \frac{1-k}{2}\tl{\ap}\ \in\ \Omega_\Cp^{p,q}
\end{align}
with the inverse
\begin{align}\label{isom_bigradings2}
\phi^{-1}:\ \bm{\ap}\ \in\ \Omega_\Cp^{p,q}\longmapsto (\text{Re}(\bm{\alpha})+\text{Im}(\bm{\ap}),\text{Re}(\bm{\alpha})-\text{Im}(\bm{\ap}))\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}.
\end{align}
The point we would like to emphasize here is that to one para-complex differential form of degree $p,q$ corresponds a {\it pair} of real forms in degrees $(p,q)$ and $(q,p)$. In particular, a para-complex form in degree $k,0$ corresponds to a pair of forms in degrees $(k,0)$ and $(0,k)$, i.e. a two $k$-forms on the two canonical para-complex foliations. Consequently, recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can easily deduce that the corresponding {\bf para-complexified Dolbeault complex} is given by
\begin{align}
\left( \Omega^{0,\bullet}_\Cp,\bar{\p}^\Cp\right),
\end{align}
In particular, the condition of holomorphicity in the para-complex coordinates $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ and $\bar{z}^i$ is equivalent to a local independence of the coordinates $\bar{z}^i$ and is therefore entirely analogous to complex geometry.

There is also an analogous map for vector (multivector) fields which we will also denote by $\phi$:
\begin{align*}
\phi&:\ (X,\tl{X})\ \in\ \XX^{(p,q)}\otimes \XX^{(q,p)}\longmapsto \frac{1+k}{2}X + \frac{1-k}{2}\tl{X}\ \in\ \XX_\Cp^{p,q}\\
\phi^{-1}&:\ \bm{X}\ \in\ \XX_\Cp^{p,q}\longmapsto (\text{Re}(\bm{X})+\text{Im}(\bm{X}),\text{Re}(\bm{X})-\text{Im}(\bm{X}))\ \in\ \XX^{(p,q)}\otimes \XX^{(q,p)}.
\end{align*}

In particular, $\phi$ maps between two copies of $\TT$ and $\TT_\Cc$

%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}

@@

\subsubsection{Lie algebroids of a para-complex manifold}\label{lie_algds_paracpx}
Here we briefly discuss what Lie algebroids the para-complex structure on a manifold $\PS$ gives rise to.
First, we recall that a Lie algebroid over $\PS$ is the triple $(E,a,\brac_E)$, where $E\rightarrow \PS$ is a vector bundle, $a: E\rightarrow T\PS$ is a bundle map and $\brac$ is a bracket operation on the sheaf of sections of $E$. The three satisfy the following:
\begin{enumerate}
\item $a([e_1,e_2]_E)=[a(e_1),a(e_2)]$, $\brac$ being the Lie bracket on $T\PS$,
\item $[e_1,fe_2]_E=f[e_1,e_2]_E+a(e_1)[f]e_2$.
\end{enumerate}

@@

If we now consider the para-complexified tangent bundle $T\PS_\Cc$, we get a para-complex Lie algebroid, which can be understood as certain sense as a {\it sum} of the two above Lie algebroids:
\begin{Ex}[Para-holomorphic tangent bundle]\label{ex:para-hol-tangent}
The $-k$-eigenbundle $T^{0,1}\subset T\PS_\Cc$ is a para-complex Lie algebroid with the bracket given by the extension of the usual Lie bracket to $T\PS_\Cc$ and restricted to $T^{0,1}$ and the anchor is again the inclusion $\imath:\  T^{0,1}\hookrightarrow T\PS_\Cc$. We can identify $T\PS_\Cc=T\oplus k T$, so that a section $X\in \XX_\Cc(\PS)$ is written as $X=U+kV=(U,V)$ for $U,V \in \XX(\PS)$ real vector fields and the Lie algebroid bracket is then given in terms of the usual Lie bracket of real vector fields as
\begin{align*}
[(U,V),(U',V')]=([U,U']+[V,V'],[U,V']+[V,U']).
\end{align*}
The Chevalley-Eilenberg complex is the para-complexified Dolbeault complex \eqref{para-dolbeault}.

There is an analogous map to \eqref{isom_bigradings2} for vector fields (which we also denote $\phi^{-1}$) mapping $X \in \XX^{0,1}_\Cc(\PS)$ to a pair of vector fields
\begin{align*}
X=(U,V) \overset{\phi^{-1}}{\mapsto} (U-V,U+V) \in \XX^{(1,0)}(\PS)\otimes \XX^{(0,1)}(\PS),
\end{align*}
realizing the $\mathbb{R}$-linear isomorphism between $T^{0,1}$ and $T\PS=L\oplus \Lt$. This map can be used to map the para-complex Lie algebroid $T^{0,1}$ to a pair of real Lie algebroids. It is a simple exercise to check that $\phi^{-1}$ in fact maps to the pair of real Lie algebroids $(L,\Lt)$ described in Example \ref{ex:real-lie-algds-on-paracpx}, so that the following diagram commutes
\begin{equation*}
\begin{tikzcd}
T^{1,0} \arrow[hookrightarrow]{d}{\imath}\arrow{r}{\phi^{-1}} & L\oplus \Lt\arrow[hookrightarrow]{d}{\imath_L\oplus\imath_\Lt}\\
TP_\Cc \arrow{r}{(\text{Re},\text{Im})} & T\oplus T
\end{tikzcd}\ .
\end{equation*}
Note, however, that $L\otimes \Lt=T$ here is not a Lie algebroid (and in particular not the tangent Lie algebroid) because the direct sum of anchors $\imath_L\oplus \imath_\Lt$ maps into $T\oplus T$ as opposed to $T$.

Consequently, the Chevalley-Eilenberg complex also splits and can be understood as a direct sum of the two complexes corresponding to $L$ and $\Lt$, as denoted in \eqref{para-dolbeault}.
\end{Ex}

@@

@@

Let us now present the main examples, examining both the real and para-complex aspects of the generalized para-complex structures.

\begin{Ex}[The trivial structure and its deformations]\label{ex:GpC_trivial}
Any manifold supports the following GpC structure
\begin{align*}
\KK_0=
\begin{pmatrix}
\id & 0 \\
0 & -\id
\end{pmatrix},
\end{align*}
that has the real $\pm 1$-eigenbundles $T$ and $T^*$ and is always integrable. The para-complexified $+k$-eigenbundle is given by
\begin{align*}
L_{\KK_0,\Cc}=\left\{\frac{1+k}{2}X+\frac{1-k}{2}\ap\mid X\in\XX(\PS),\ \ap \in \Omega(\PS)\right\}.
\end{align*}

 The following two GpC structures can be seen as deformations of $\KK_0$ by either a two-form $b$ or a bi-vector $\beta$:
\begin{align*}
\KK_b=
\begin{pmatrix}
\id & 0 \\
2b & -\id
\end{pmatrix},\quad
\KK_\beta=
\begin{pmatrix}
\id & 2\beta \\
0 & -\id
\end{pmatrix}.
\end{align*} 
$\KK_b$ is integrable iff $\rd b =-H$, and its eigenbundles are $L_{\KK_b} = \text{graph}(b)=\{X+b(X)\mid X \in \XX\}$ and $\widetilde{L}_{\KK_b} =T^*$. Similarly, $\KK_\beta$ is integrable iff $\beta$ is a Poisson structure, (see \cite[Lemma~2.13]{Hu:2019zro}) and its eigenbundles are $L_{\KK_\beta} =T$ and $\widetilde{L}_{\KK_\beta} =\text{graph}(-\beta)=\{\ap-\beta(\ap)\mid \ap \in \Omega\}$.
The Lie algebroid given by $\widetilde{L}_{\beta}$ is equivalent to the Poisson Lie algebroid, i.e. it can be understood as a Lie algebroid with the underlying bundle $T^*$ and the anchor given by the Poisson bivector $\beta : T^* \to T$.

The para-complexified GpC structure $\KK_{b,\Cc}$ has the $+k$-eigenbundle
\begin{align*}
L_{\KK_b,\Cc}=\left\{\frac{1+k}{2}(X+b(X))+\frac{1-k}{2}\ap\mid X\in\XX(\PS),\ \ap \in \Omega(\PS)\right\},
\end{align*}
and similarly $\KK_{\bt,\Cc}$ has the $+k$-eigenbundle
\begin{align*}
L_{\KK_\bt,\Cc}=\left\{\frac{1+k}{2}X+\frac{1-k}{2}(\ap-\bt(\ap))\mid X\in\XX(\PS),\ \ap \in \Omega(\PS)\right\}.
\end{align*}
\end{Ex}

\begin{Ex}[Para-complex structures]\label{ex: pc}
An almost para-complex structure $K\in \Endo(T)$, defines the diagonal generalized almost para-complex structure:
\begin{align*}
\KK_K=
\begin{pmatrix}
K & 0 \\
0 & -K^*
\end{pmatrix}.
\end{align*}
The integrability of $\KK_K$ is equivalent to Frobenius integrability of $K$ , i.e. vanishing of the Nijenhuis tensor of $K$.
Thus a para-complex structure defines a generalized para-complex structure of the above form. 
The corresponding Dirac structures are given by the $+1$ eigenbundle $L_{\KK_K}=T^{(1,0)}\oplus T^{*(0,1)}$ and $-1$ eigenbundle $\widetilde{L}_{\KK_K} =T^{(0,1)}\oplus T^{*(1,0)}$, where the bigrading is with respect to $K$. The $+k$-eigenbundle of the para-complexified GpC structure is $L_{\KK_K}=T^{1,0}\oplus T^{*0,1}$, where the bigrading is now the para-complex one.
%
%The structure $\KK_P$ can be generalized to the following
%\begin{align*}
%\KK=
%\begin{pmatrix}
%P & \Pi \\
%\Omega & -P^*
%\end{pmatrix},
%\end{align*}
%where we can read off from the constraints in \eqref{eq:GpC_generalform} that $P^2=\id$ implies that $\Pi\Omega=0$ and both $\Pi$ and $\Omega$ have to be of type $(2,0)+(0,2)$ with respect to the grading given by $P$.
\end{Ex}

\begin{Ex}[Symplectic structures]\label{ex:GpC_sympl}
A pre-symplectic form $\omega$ defines the anti-diagonal almost generalized para-complex structure
\begin{align*}
\KK_\omega=
\begin{pmatrix}
0 & \omega^{-1} \\
\omega & 0
\end{pmatrix}.
\end{align*}
The integrability of $\KK_\omega$ is equivalent to $\rd\omega=0$.
Thus, if $\omega$ is symplectic then $\KK_\omega$ is a generalized para-complex structure.
The $\pm 1$ eigenbundles are given by $\text{graph}(\pm\omega)=\{X\pm\omega(X)\mid X\in \XX\}$ and the $+k$-eigenbundle is given by $\text{graph}(+k\omega)$.
\end{Ex}

\paragraph{Comparision with generalized complex geometry}
We see that two of the main examples given by the symplectic (Example \ref{ex:GpC_sympl}) and para-complex (Example \ref{ex: pc}) structures are in the para-complexified form directly analogous to the symplectic and complex examples of generalized complex (GC) structures \cite{Gualtieri:2003dx}. However, we can also again see the distinguishing feature of para-complex geometry ensuring that the para-complex Dirac structure always corresponds to the pair of real Dirac structures and the correspondence is given by the isomorphism $\phi$ described in Section \ref{sec:isomorphism}.

Furthermore, while almost GC structures exist only on almost complex manifolds \cite{Gualtieri:2003dx}, Example \ref{ex:GpC_trivial} demonstrates that GpC structures exist on any Poisson manifold and in particular on any smooth manifold (with trivial Poisson structure). Another feature of GpC geometry that is not present in GC geometry is that the GpC structures can be half-integrable (similarly to ordinary para-complex structures): see the cases of $\KK_b$ and $\KK_\beta$ from Example \ref{ex:GpC_trivial} which are always at least half integrable and are fully integrable iff $b$ is closed and $\beta$ is Poisson, respectively. On the other hand, $\KK_\omega$ in Example \ref{ex:GpC_sympl} can only be half-integrable when the $H$-flux is non-zero.

@@

In this section we will see how to associate a class of $2D$ topological field theories to generalized para-complex structures.
The construction follows the philosophy of \cite{Pestun:2006rj}, where $2D$ topological theories are constucted purely from the data of a generalized complex structures \cite{Gualtieri:2003dx}. Rather than constructing the theory from the Lie bi-algebroid defined by the generalized structure, we simply recover the $2D$ theory as a boundary theory of the (trivial) $3D$ topological model of the underlying exact Courant algebroid, defined by a Dirac structure. In this sense, our construction is similiar to the one presented in \cite{Cattaneo:2009zx} with the difference that we mainly focus on the para-complex aspects. For another class of $2D$ boundary theories to the $3D$ Courant algebroid $\sigma$-model see \cite{SeveraTduality}. A different approach to a construction of $2D$ theories from Dirac structures, see \cite{KSSdirac}.

The prescription of defining the $2D$ topological theory associated to a generalized para-complex structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
More generally, this $3D$ theory can be defined for any Courant algebroid on $M$ \cite{Roytenberg:2002nu}, but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
The key to our construction is to realize the data of a generalized para-complex structure in terms of its eigenbundles, which are Dirac structures in the real Courant algebroid $\TT$.
In this way, we obtain a pair of (real) Dirac structures $L, \Tilde{L}$ corresponding to the $\pm$ eigenbundles of the generalized para-complex structure.

@@

By similar reasoning, one can obtain a single $2D$ TFT from the data of a generalized para-complex structure. 
One considers the para-complexification $(\TT) \otimes_{\RR} \Cc$ of the standard Courant algebroid. 
The real Dirac structures $L, \Tilde{L}$ combine to give a para-complex Dirac structure $L_\Cc$. 
In turn, we obtain a single $2D$ TFT defined over the para-complex numbers. This approach more closely resembles to the one of \cite{Cattaneo:2009zx}, where this was done for generalized complex structures, from which one recovers a complex Dirac structure $L_\mathbb{C}\subset (\TT) \otimes_{\RR} \mathbb{C}$. The interesting property of para-complex structures which one cannot see in the complex case is that the para-complex Dirac structure $L_\Cc$ corresponds to a pair of real Dirac structures and therefore represents a certain {\it double} on the level of the $2D$ theories.

@@

From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
We recall the construction of the $3D$ topological field theory from the data of a Courant algebroid. 
For more details, see \cite{Roytenberg:2002nu, Cattaneo:2009zx}.

@@

We begin by setting up our model for the theory of derived manifolds \david{dg manifolds?}, which is a well-behaved class of $NQ$ manifolds appropriate for setting up quantization of $\sigma$-models (see for instance \cite{CostelloSUSY}). 
A dg manifold is a pair $\cN = (N, \sA^\bullet_\cN)$ where $N$ is a smooth manifold, called the body, and $\sA^\bullet_\cN$ a sheaf of graded commutative algebras over the de Rham complex $\Omega^\bullet_N$.
Here, $\d_\cN$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
\begin{itemize}
\item[(1)] $\sA_\cN$ is concentrated in finitely many degrees;
\item[(2)] For each $k$, $\sA^k_\cN$ is a locally free sheaf of $C^\infty_N$-modules of finite rank;
\item[(3)] The differential $\d_N : \sA_\cN^\bullet \to \sA_\cN^{\bullet+1}$ is square zero differential operator making $(\sA_\cN , \d_\cN)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^\bullet_N$.
\end{itemize}

In particular, as a graded algebra $\sA^\bullet_\cN$ is given by functions on the total space of some graded vector bundle $A_\cN$ on $N$ (which is of finite rank and concentrated in finitely many degrees). 
In the language of $NQ$ manifolds, the homological vector field defining the $Q$-structure is $\d_\cN$.

@@

\begin{remark}
In \cite{PymSafronov} it was shown that a more general class of $2$-shifted symplectic derived spaces, called $L_\infty$ algebroids, are equivalent to {\em twisted} Courant algebroids. 
This is similar to a Courant algebroid, where the Jacobi identity only holds up to homotopy given by some closed $4$-form. Note that this twisting is $1$-degree higher in the $L_\infty$ hierarchy than the usual closed $3$-form \v{S}evera class of the exact Courant algebroids.
\end{remark}

@@

From here on, to any Courant algebroid $E$ on a manifold $M$ we associate the dg manifold $X_E$ which carries a $2$-shifted symplectic structure. 
In the case that the Courant algebroid is exact, we denote the associated $2$-shifted symplectic space $X_H$, where $H$ labels the \v{S}evera class.

We first review some basic examples of AKSZ theories associated to Courant algebroids. 
The simplest type of Courant algebroid is the one over a point, described in Example \ref{Ex: point}. 
The resulting AKSZ theory is a familiar one.
